Reply To Examiners

### 2014-04-27 answer_thesis_examiner/chap1.tex
auto

>>>>

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
4 & 5 & missing references & citation added \\
4 & 8 & missing references & citation added \\
5 & 13 & techniques ... has & techniques ... have \\
6 & 5 & many fold & manyfold \\
14 & Eq 2.1 & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{\frac{A_x^2}{\sigma^2}}$ & $pdf(A_x)=\frac{1}{\sqrt{\pi}\sigma} e^{-\frac{A_x^2}{\sigma^2}}$ \\
\end{longtable}

\rowcolors{1}{white}{}
\replyToComment
    {Page 14: With reference to Equations 2.1, 2.2, 2.3 what are the range of $A_x$, $A$ and $I$}
    {The range of $A_x$ is from $(-\infty, \infty)$, and the range of both $A$ and $I$ is from $(0,\infty)$}

\replyToComment
  {Page 14: Does the integration of pdf for $A_x,A,I$ sum to 1?}
  {With the defined range above, YES they are all sum to 1. This is easy to verify as they belong to the classes of Normal, Chi-Squared (2 degree-of-freedom) and Exponential Distribution respectively.}

\rowcolors{2}{gray!25}{white}    
\noindent
\begin{longtable}[c]{p{0.1\textwidth}|p{0.1\textwidth}|p{0.3\textwidth}|p{0.3\textwidth}}
\textbf{Page} & \textbf{Line} & \textbf{Gramatical Errors} & \textbf{Corrections} \\
 \hline
 \endhead
15 & 6 & missing explaination for $E,B$ & explaination added \\
\end{longtable}
